---
title: "vignette_get_kolada_data"
author: "Ana Stanojcic and Sofia Danielson"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette_get_kolada_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
library(lab5)  

Introduction
This vignette demonstrates how to use the get_kolada_data() function from the lab5 package. The function interacts with the Kolada API, which provides data on Swedish municipalities' performance in various areas, such as healthcare, education, and sustainability.

We will show how to retrieve data for a specific KPI (Key Performance Indicator), municipality, and year using the get_kolada_data() function. 

# Example usage
kpi <- "N02799"  # Number of children born per 1000
municipality <- "0180"  # Stockholm's municipality ID
year <- "2020"

# Fetch data from Kolada API
data <- get_kolada_data(kpi, municipality, year)

# Display the returned data structure
str(data)


#Explanation of the output:
The returned data typically contains:
count: The number of entries returned by the API;
values: A list of data frames with the KPI values for the specified municipality and year

#Conclusion
We showed how to get data for a specific municipality, KPI and year

```{r setup}
library(lab5)
```
