---
title: "vignette_get_municipality_id"
author: "Ana Stanojcic and Sofia Danielson"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette__get_municipality_id}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(lab5)
```

library(lab5)  

#Introduction
This vignette demonstrates how to use the get_municipality_id() function from the lab5 package. The function interacts with the Kolada API, which provides data on Swedish municipalities' performance in different areas, such as healthcare, education, and sustainability.

The function retrieves the unique ID for a municipality from the Kolada API based on its name, using the get_municipality_id() function.

#Example Usage
## Fetch municipality ID for Lund
```{r}
municipality_name <- "Lund"
municipality_id <- get_municipality_id(municipality_name)
print(paste("The municipality ID for", municipality_name, "is", municipality_id))

```


#Conclusion
This vignette demonstrated how to use the get_municipality_id() function to get the unique identifier for a municipality from the Kolada API. This identifier can be used in other API calls to retrieve specific performance data for the municipality.


